Parameterized convection, grid-scale clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-17 resolution.tex
edits

To unravel the contributions of $\omega$ and $q$ at the 850 hPa level, $\omega_{850}$ and $q_{850}$ to the increase in climatological stratiform precipitation with resolution, the area averaged, climatological stratiform precipitation rate $\overline{R_{s}}$ is decomposed into a time mean magnitude term $M$ and space-time frequency term $f$,
\begin{equation}
\overline{R_{s}} = \sum_i \sum_j f \left( \omega_i , q_j \right) M \left( \omega_i , q_j \right) \label{eq:pdecomp}
\end{equation}
after \cite{TETAL2018CD}, and the subscript $850$ is dropped from $\omega$ and $q$ for brevity. Table~\ref{tbl:table2} indicates that the $\pm 15^{\circ}$ latitude band accounts for most of the change in global mean stratiform precipitation with resolution, and so Figure~\ref{fig:pdecomp} is a plot of the terms $M\left( \omega_i , q_j \right)$ and $f\left( \omega_i , q_j \right) \times M\left( \omega_i , q_j \right)$ for all resolutions, and in the $\pm 15^{\circ}$ latitude region. The plots are computed using 6-hourly instantaneous output of $\omega_{i}$ and $q_{j}$, with 0.05 Pa/s and 0.4 g/kg bins. Values in  $\left( \omega_{i} , q_{j} \right)$ space are only shown for bins with $f \geq1 \times 10^{-5}$, a reasonable cut-off to a bins' contribution to $\overline{R_s}$. Larger $\omega$ values correspond to larger magnitude stratiform precipitation rates, which have larger space-time frequencies $f\left( \omega_i , q_j \right)$ at higher resolutions, explaining the increase in $\overline{R_{s}}$ with resolution in Table~\ref{tbl:table2}. Changes in the space-time frequency of the $q$ field contributes comparatively less to changes in stratiform precipitation.

>>>>

To unravel the contributions of $\omega$ and $q$ at the 850 hPa level, $\omega_{850}$ and $q_{850}$ to the increase in climatological stratiform precipitation with resolution, the area averaged, climatological stratiform precipitation rate $\overline{R_{s}}$ is decomposed into a time mean magnitude term $M$ and space-time frequency term $f$,
\begin{equation}
\overline{R_{s}} = \sum_i \sum_j f \left( \omega_i , q_j \right) M \left( \omega_i , q_j \right) \label{eq:pdecomp}
\end{equation}
after \cite{TETAL2018CD}, and the subscript $850$ is dropped from $\omega$ and $q$ for brevity.

Table~\ref{tbl:table2} indicates that the $\pm 15^{\circ}$ latitude band accounts for most of the change in global mean stratiform precipitation with resolution. Figure~\ref{fig:pdecomp} is a plot of the terms $M\left( \omega_i , q_j \right)$ and $f\left( \omega_i , q_j \right) \times M\left( \omega_i , q_j \right)$ for all resolutions, and in the $\pm 15^{\circ}$ latitude region. The plots are computed using 6-hourly instantaneous output of $\omega_{i}$ and $q_{j}$, with 0.05 Pa/s and 0.4 g/kg bins. Values in  $\left( \omega_{i} , q_{j} \right)$ space are only shown for bins with $f \geq1 \times 10^{-5}$, a reasonable cut-off to a bins' contribution to $\overline{R_s}$. Larger $\omega$ values correspond to larger magnitude stratiform precipitation rates, which have larger space-time frequencies $f\left( \omega_i , q_j \right)$ at higher resolutions, explaining the increase in $\overline{R_{s}}$ with resolution in Table~\ref{tbl:table2}. Changes in the space-time frequency of the $q$ field contributes comparatively less to changes in stratiform precipitation.
